### 2011-08-15 doc/theses/vitasek/diplomka.tex
Thesis: in progress.

The pseudocode of this CH (taken from the original article with trivial modifications without changing the logic) is in Listing \ref{ch-fidax}.

\begin{algorithm}
\caption{FIDAX CH}
\label{ch-fidax}
\begin{algorithmic}
\REQUIRE $C$ list of candidate AMs
\ENSURE a feasible solution
\STATE $C' \gets C$ sorted by decreasing size
\STATE Compute the weight $w(m)$ of each $m$ in $C$
\FORALL{$t$ in $\Sigma^E$}
  \STATE Let $m$ be a \textbf{highest-weight} mapping of type $t$ in $C'$
  \STATE Remove from $C'$ all mappings of type $t$ except $m$
\ENDFOR
\FORALL{$m$ in $C'$}
  \STATE $S \gets$ all mappings in $C$ whose images intersect $\iota(m)$
  \IF{$w(m) > \sum_{p \in S} w(p)$}
    \STATE remove all $p \in S$ from $C'$
  \ELSE
    \STATE remove $m$ from $C'$
  \ENDIF
\ENDFOR
\RETURN $C'$
\end{algorithmic}
\end{algorithm}

@@

See the Listing \ref{ch-random} for its pseudocode.

\begin{algorithm}
\caption{Random CH}
\label{ch-random}
\begin{algorithmic}
\REQUIRE $N$ required size of pool
\REQUIRE $C$ list of candidate AMs
\ENSURE pool of $N$ feasible solutions
\STATE $r \gets $ empty pool
\FOR{$i = 1 \to N$} 
  \STATE \COMMENT{create 1 solution}
  \STATE $s \gets $ empty solution
  \WHILE{$s$ is a feasible ID set}
    \STATE $a \gets $ pick at random from $C \backslash S$
    \STATE $s \gets s \cup a$
  \ENDWHILE
  \STATE $r \gets r \cup s$
\ENDFOR
\RETURN $r$
\end{algorithmic}
\end{algorithm}

@@

Again, this is a hungry heuristic, the Listing \ref{ch-fuzzy} contains its pseudocode.

@@

\begin{algorithm}
\caption{Fuzzy CH}
\label{ch-fuzzy}
\begin{algorithmic}
\REQUIRE $N$ required size of pool
\REQUIRE $C$ list of candidate AMs
\ENSURE pool of $N$ feasible solutions
\STATE $r \gets $ empty pool
\FOR{$i = 1 \to N$} 
  \STATE \COMMENT{create 1 solution}
  \STATE $s \gets $ empty solution
  \STATE $C' \gets C$

@@

See listing \ref{ch-incremental}.

\begin{algorithm}
\caption{Incremental CH}
\label{ch-incremental}
\begin{algorithmic}
\REQUIRE $C$ list of candidate AMs
\ENSURE a feasible solution
\STATE $C' \gets $ sort $C$ by decreasing weight
\STATE $s \gets $ empty solution
\FORALL{$c \in C'$}
  \IF{$s \cup c$ is a feasible ID set}
    \STATE $s \gets s + c$
  \ENDIF
\ENDFOR
\RETURN $s$
\end{algorithmic}
\end{algorithm}

@@

See listing \ref{ch-removal}.

\begin{algorithm}
\caption{Removal CH}
\label{ch-removal}
\begin{algorithmic}
\REQUIRE $C$ list of candidate AMs
\ENSURE a feasible solution
\STATE $C' \gets $ sort $C$ by increasing weight
\STATE $s \gets C'$
\FORALL{$c \in s$}
  \IF{$s$ is a feasible ID set}
    \RETURN $s$
  \ENDIF
  \STATE $s \gets s \backslash c$
\ENDFOR
\end{algorithmic}
\end{algorithm}

@@

This ultimately trivial improvement heuristics does nothing. It simply returns the feasible pool unchanged. For the sake of completeness, see its listing \ref{ih-identity}.

\begin{algorithm}
\caption{Identity IH}
\label{ih-identity}
\begin{algorithmic}
\REQUIRE $FP$ pool of feasible solutions
\ENSURE the same pool of feasible solutions
\RETURN $FP$
\end{algorithmic}
\end{algorithm}

@@

See listing \ref{ih-removeworst}.

\begin{algorithm}
\caption{Remove Worst IH}
\label{ih-removeworst}
\begin{algorithmic}
\REQUIRE $FP$ pool of feasible solutions
\ENSURE pool of feasible solutions
\STATE $s_{min} \gets $ solution with the lowest weight $\in FP$
\RETURN $FP \backslash s_{min}$
\end{algorithmic}
\end{algorithm}

@@

See listing \ref{ih-randomremove}.

\begin{algorithm}
\caption{Random Remove IH}
\label{ih-randomremove}
\begin{algorithmic}
\REQUIRE $FP$ pool of feasible solutions
\REQUIRE $k \in (0,1)$ ratio of AMs to remove from each $s \in FP$
\ENSURE pool of feasible solutions
\FORALL{$s \in FP$}
  \STATE $K \gets k * |s|$
  \STATE remove $K$ random AMs from $s$
\ENDFOR
\RETURN $FP$
\end{algorithmic}
\end{algorithm}

@@

\heu{Hungry} tries to improve each solution in the feasible pool in the following way. It orders all candidate AMs not present in the solution by decreasing weight. Afterwards, it iteratively tries to extend the solution with these AMs, taking care not to violate the ID set condition. The resulting solution (whether any AMs were added or not) is then returned to the pool. Listing \ref{ih-hungry} captures this process.

\begin{algorithm}
\caption{Hungry IH}
\label{ih-hungry}
\begin{algorithmic}
\REQUIRE $FP$ pool of feasible solutions
\REQUIRE $C$ list of candidate AMs
\ENSURE pool of feasible solutions
\FORALL{$s \in FP$}
  \STATE \COMMENT {improve a single solution}
  \STATE $C' \gets C \backslash s$
  \STATE $C' \gets C'$ sorted by decreasing weight
  \FORALL{$c \in C'$}
    \IF{$s \cup c$ is a feasible ID set}
      \STATE $s \gets s \cup c$
    \ENDIF
  \ENDFOR
\ENDFOR
\RETURN $FP$
\end{algorithmic}
\end{algorithm}

@@

See listing \ref{ih-mutation}.

\begin{algorithm}
\caption{Mutation IH}
\label{ih-mutation}
\begin{algorithmic}
\REQUIRE $FP$ pool of feasible solutions
\REQUIRE $k$ ratio of AMs to fix
\ENSURE pool of feasible solutions
\STATE $incumbent \gets $ best solution in $FP$ \COMMENT {best = highest weight}
\STATE $K \gets k * |incumbent|$
\STATE fix $K$ random AMs from $incumbent$ in GLPK problem formulation
\STATE $improved \gets $ run GLPK
\RETURN $FP \cup improved$
\end{algorithmic}
\end{algorithm}

@@

See listing \ref{ih-crossover}.

\begin{algorithm}
\caption{Crossover IH}
\label{ih-crossover}
\begin{algorithmic}
\REQUIRE $FP$ pool of feasible solutions
\REQUIRE $k$ ratio of solutions to look for commonalities in
\ENSURE pool of feasible solutions
\STATE $K \gets k * |FP|$
\STATE $FP' \gets K$ random solutions $\in FP$
\STATE $am \gets$ AMs found in all solutions $\in FP'$
\STATE fix $am$ in GLPK problem formulation
\STATE $improved \gets $ run GLPK
\RETURN $FP \cup improved$
\end{algorithmic}
\end{algorithm}

@@

See listing \ref{ih-localbranching}.

\begin{algorithm}
\caption{Local Branching IH}
\label{ih-localbranching}
\begin{algorithmic}
\REQUIRE $FP$ pool of feasible solutions
\REQUIRE $k$ ratio of total AM count to bound the Hamming distance to
\ENSURE pool of feasible solutions
\STATE $K \gets k * |$total AM count$|$
\STATE $incumbent \gets $ best solution in $FP$ \COMMENT {best = highest weight}
\STATE add max Hamming distance requirement to GLPK problem formulation
\STATE $improved \gets $ run GLPK
\RETURN $FP \cup improved$
\end{algorithmic}
\end{algorithm}

>>>>

The pseudocode of this CH (taken from the original article with trivial modifications without changing the logic) is in Listing \ref{listing-ch-fidax}.

\begin{algorithm}
\caption{FIDAX CH}
\label{listing-ch-fidax}
\begin{algorithmic}
\REQUIRE $C$ list of candidate AMs
\ENSURE a feasible solution
\STATE $C' \gets C$ sorted by decreasing size
\STATE Compute the weight $w(m)$ of each $m$ in $C$
\FORALL{$t$ in $\Sigma^E$}
  \STATE Let $m$ be a \textbf{highest-weight} mapping of type $t$ in $C'$
  \STATE Remove from $C'$ all mappings of type $t$ except $m$
\ENDFOR
\FORALL{$m$ in $C'$}
  \STATE $S \gets$ all mappings in $C$ whose images intersect $\iota(m)$
  \IF{$w(m) > \sum_{p \in S} w(p)$}
    \STATE remove all $p \in S$ from $C'$
  \ELSE
    \STATE remove $m$ from $C'$
  \ENDIF
\ENDFOR
\RETURN $C'$
\end{algorithmic}
\end{algorithm}

@@

See the Listing \ref{listing-ch-random} for its pseudocode.

\begin{algorithm}
\caption{Random CH}
\label{listing-ch-random}
\begin{algorithmic}
\REQUIRE $N$ required size of pool
\REQUIRE $C$ list of candidate AMs
\ENSURE pool of $N$ feasible solutions
\STATE $r \gets $ empty pool
\FOR{$i = 1 \to N$} 
  \STATE \COMMENT{create 1 solution}
  \STATE $s \gets $ empty solution
  \WHILE{$s$ is a feasible ID set}
    \STATE $a \gets $ pick at random from $C \backslash S$
    \STATE $s \gets s \cup a$
  \ENDWHILE
  \STATE $r \gets r \cup s$
\ENDFOR
\RETURN $r$
\end{algorithmic}
\end{algorithm}

@@

Again, this is a hungry heuristic, the Listing \ref{listing-ch-fuzzy} contains its pseudocode.

@@

\begin{algorithm}
\caption{Fuzzy CH}
\label{listing-ch-fuzzy}
\begin{algorithmic}
\REQUIRE $N$ required size of pool
\REQUIRE $C$ list of candidate AMs
\ENSURE pool of $N$ feasible solutions
\STATE $r \gets $ empty pool
\FOR{$i = 1 \to N$} 
  \STATE \COMMENT{create 1 solution}
  \STATE $s \gets $ empty solution
  \STATE $C' \gets C$

@@

See listing \ref{listing-ch-incremental}.

\begin{algorithm}
\caption{Incremental CH}
\label{listing-ch-incremental}
\begin{algorithmic}
\REQUIRE $C$ list of candidate AMs
\ENSURE a feasible solution
\STATE $C' \gets $ sort $C$ by decreasing weight
\STATE $s \gets $ empty solution
\FORALL{$c \in C'$}
  \IF{$s \cup c$ is a feasible ID set}
    \STATE $s \gets s + c$
  \ENDIF
\ENDFOR
\RETURN $s$
\end{algorithmic}
\end{algorithm}

@@

See listing \ref{listing-ch-removal}.

\begin{algorithm}
\caption{Removal CH}
\label{listing-ch-removal}
\begin{algorithmic}
\REQUIRE $C$ list of candidate AMs
\ENSURE a feasible solution
\STATE $C' \gets $ sort $C$ by increasing weight
\STATE $s \gets C'$
\FORALL{$c \in s$}
  \IF{$s$ is a feasible ID set}
    \RETURN $s$
  \ENDIF
  \STATE $s \gets s \backslash c$
\ENDFOR
\end{algorithmic}
\end{algorithm}

@@

This ultimately trivial improvement heuristics does nothing. It simply returns the feasible pool unchanged. For the sake of completeness, see its listing \ref{listing-ih-identity}.

\begin{algorithm}
\caption{Identity IH}
\label{listing-ih-identity}
\begin{algorithmic}
\REQUIRE $FP$ pool of feasible solutions
\ENSURE the same pool of feasible solutions
\RETURN $FP$
\end{algorithmic}
\end{algorithm}

@@

See listing \ref{listing-ih-removeworst}.

\begin{algorithm}
\caption{Remove Worst IH}
\label{listing-ih-removeworst}
\begin{algorithmic}
\REQUIRE $FP$ pool of feasible solutions
\ENSURE pool of feasible solutions
\STATE $s_{min} \gets $ solution with the lowest weight $\in FP$
\RETURN $FP \backslash s_{min}$
\end{algorithmic}
\end{algorithm}

@@

See listing \ref{listing-ih-randomremove}.

\begin{algorithm}
\caption{Random Remove IH}
\label{listing-ih-randomremove}
\begin{algorithmic}
\REQUIRE $FP$ pool of feasible solutions
\REQUIRE $k \in (0,1)$ ratio of AMs to remove from each $s \in FP$
\ENSURE pool of feasible solutions
\FORALL{$s \in FP$}
  \STATE $K \gets k * |s|$
  \STATE remove $K$ random AMs from $s$
\ENDFOR
\RETURN $FP$
\end{algorithmic}
\end{algorithm}

@@

\heu{Hungry} tries to improve each solution in the feasible pool in the following way. It orders all candidate AMs not present in the solution by decreasing weight. Afterwards, it iteratively tries to extend the solution with these AMs, taking care not to violate the ID set condition. The resulting solution (whether any AMs were added or not) is then returned to the pool. Listing \ref{listing-ih-hungry} captures this process.

\begin{algorithm}
\caption{Hungry IH}
\label{listing-ih-hungry}
\begin{algorithmic}
\REQUIRE $FP$ pool of feasible solutions
\REQUIRE $C$ list of candidate AMs
\ENSURE pool of feasible solutions
\FORALL{$s \in FP$}
  \STATE \COMMENT {improve a single solution}
  \STATE $C' \gets C \backslash s$
  \STATE $C' \gets C'$ sorted by decreasing weight
  \FORALL{$c \in C'$}
    \IF{$s \cup c$ is a feasible ID set}
      \STATE $s \gets s \cup c$
    \ENDIF
  \ENDFOR
\ENDFOR
\RETURN $FP$
\end{algorithmic}
\end{algorithm}

@@

See listing \ref{listing-ih-mutation}.

\begin{algorithm}
\caption{Mutation IH}
\label{listing-ih-mutation}
\begin{algorithmic}
\REQUIRE $FP$ pool of feasible solutions
\REQUIRE $k$ ratio of AMs to fix
\ENSURE pool of feasible solutions
\STATE $incumbent \gets $ best solution in $FP$ \COMMENT {best = highest weight}
\STATE $K \gets k * |incumbent|$
\STATE fix $K$ random AMs from $incumbent$ in GLPK problem formulation
\STATE $improved \gets $ run GLPK
\RETURN $FP \cup improved$
\end{algorithmic}
\end{algorithm}

@@

See listing \ref{listing-ih-crossover}.

\begin{algorithm}
\caption{Crossover IH}
\label{listing-ih-crossover}
\begin{algorithmic}
\REQUIRE $FP$ pool of feasible solutions
\REQUIRE $k$ ratio of solutions to look for commonalities in
\ENSURE pool of feasible solutions
\STATE $K \gets k * |FP|$
\STATE $FP' \gets K$ random solutions $\in FP$
\STATE $am \gets$ AMs found in all solutions $\in FP'$
\STATE fix $am$ in GLPK problem formulation
\STATE $improved \gets $ run GLPK
\RETURN $FP \cup improved$
\end{algorithmic}
\end{algorithm}

@@

See listing \ref{listing-ih-localbranching}.

\begin{algorithm}
\caption{Local Branching IH}
\label{listing-ih-localbranching}
\begin{algorithmic}
\REQUIRE $FP$ pool of feasible solutions
\REQUIRE $k$ ratio of total AM count to bound the Hamming distance to
\ENSURE pool of feasible solutions
\STATE $K \gets k * |$total AM count$|$
\STATE $incumbent \gets $ best solution in $FP$ \COMMENT {best = highest weight}
\STATE add max Hamming distance requirement to GLPK problem formulation
\STATE $improved \gets $ run GLPK
\RETURN $FP \cup improved$
\end{algorithmic}
\end{algorithm}
